Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-28 Markdown Documents/Manuscript.Rmd
moved a bunch of stuff to supplemental

We then used this to predict what the fees would have been for every year we didn't have
```{r cache=TRUE, include=FALSE}
fillData<-FEdat[,1:2]

@@

## 3.3. Model Validation
To assess the validity of our model, we used a k-fold cross validation technique.

@@

# 5. Supplemental

>>>>

@@

# S. Supplemental

## S.1. Visitation Fee Back Predicting Accuracy
We then used this to predict what the fees would have been for every year we didn't have
```{r cache=TRUE, include=FALSE}

FEdat<-read.csv("~/SmokeProject/Data/LauraStoddardEntryFeeCsv.csv")
FEdat<-FEdat %>% dplyr::select(Park,Year,SingleVisitorEntryFee) #keep only these columns

d<-na.omit(FEdat) #get rid of rows with any NA

fillData<-FEdat[,1:2]

## S.2. Model Validation Process

## S.3. Model Validation Results
To assess the validity of our model, we used a k-fold cross validation technique.

@@
